An Abstraction-based Approach to Network Synthesis

### 2016-11-03 paper/abstraction/paper.tex
add incrementality section

\begin{figure*}[t!]
  \begin{minipage}[t]{.54\linewidth}
    \hdr{Concrete Configuration}{}
    \begin{code}
      \Router{S1}
        Match[100] \PREFIX=GP1, \PEER=*
          \PEER \Arrow *
        Match[100] \PREFIX=GP2, \PEER=*
          \PEER \Arrow *
        ...
        Match[100] \PREFIX=LP1, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow \{AG1, ..., AL1, ...\}
        Match[100] \PREFIX=LP2, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow \{AG1, ..., AL1, ...\}
        ...
        Match[110] \PREFIX=0.0.0.0/[0..32], \PEER=P1, 
          \PEER \Arrow *, \COMM \Arrow (1,0)
        Match[100] \PREFIX=0.0.0.0/[0..32], \PEER=P2, 
          \PEER \Arrow *, \COMM \Arrow (0,1)
        ...
      \end{code}
  \end{minipage}
  %
  \begin{minipage}[t]{.4\linewidth}
    \hdr{Template Configuration}{}
    \begin{code}
      \Router{S}
        Match[100] \PREFIX=\$GP, \PEER=*
          \PEER \Arrow *
        Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
          \PEER \Arrow \{AG, AL\}
        Match[110] 0.0.0.0/[0..32], \PEER=P1, 
          \PEER \Arrow *, \COMM \Arrow (1,0)
        Match[100] 0.0.0.0/[0..32], \PEER=P2, 
          \PEER \Arrow *, \COMM \Arrow (0,1)
        ...
      \end{code}
  \end{minipage}%

@@

  \caption{Spine configurations for concrete and abstract policies.}
  \label{fig:bgp-configs}
\end{figure*}

By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy. Figure~\ref{fig:bgp-configs} shows partial a configuration for the spine routers in the concrete and abstract policies.

@@

>>>>

\begin{figure*}[t!]
  \begin{minipage}[t]{.54\linewidth}
    \hdr{Concrete Configuration}{}
    \begin{code}
      \Router{S1, S2}
        Match[100] \PREFIX=GP1, \PEER=*
          \PEER \Arrow *
        Match[100] \PREFIX=GP2, \PEER=*
          \PEER \Arrow *
        ...
        Match[100] \PREFIX=LP1, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow \{AG1, ..., AL1, ...\}
        Match[100] \PREFIX=LP2, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow \{AG1, ..., AL1, ...\}
        ...
        Match[110] \PREFIX=0.0.0.0/[0..32], \PEER=P1, 
          \PEER \Arrow *, \COMM \Arrow (1,0)
        Match[100] \PREFIX=0.0.0.0/[0..32], \PEER=P2, 
          \PEER \Arrow *, \COMM \Arrow (0,1)
        ...
      \end{code}
  \end{minipage}
  %
  \begin{minipage}[t]{.4\linewidth}
    \hdr{Template Configuration}{}
    \begin{code}
      \Router{S}
        Match[100] \PREFIX=\$GP, \PEER=*
          \PEER \Arrow *
        Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
          \PEER \Arrow \{AG, AL\}
        Match[110] 0.0.0.0/[0..32], \PEER=P1, 
          \PEER \Arrow *, \COMM \Arrow (1,0)
        Match[100] 0.0.0.0/[0..32], \PEER=P2, 
          \PEER \Arrow *, \COMM \Arrow (0,1)
        ...
      \end{code}
  \end{minipage}%

@@

  \caption{Spine configurations for concrete and abstract policies. \ryan{TODO: this would look good in powerpoint and by connecting related components}}
  \label{fig:bgp-configs}
\end{figure*}

By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy. Figure~\ref{fig:bgp-configs} shows part of the configuration for the spine routers for the concrete and abstract policies.

The spine switches have a default rule for the prefix $0.0.0.0/[0..32]$ that will match advertisements from peer $P1$ and $P2$. The match for $P1$ is preferred since it has a higher BGP local-preference attribtue (110). If an advertisement from $P1$ is available the spine attaches the community tag $(1,0)$ and advertises the route to all its peers. If only an advertisement from the backup $P2$ is available, then it attaches the tag $(0,1)$ and advertises this to all peers instead.

In the template configuration, it will have additional policy for the local and global prefixes. It will match any global prefix from any peer and re-advertise the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to all other internal peers. The concrete configurations will have a similar configuration for each local and global prefix.

@@

\subsection{Incrementality}

Suppose that we want to expand the concrete datacenter by adding an additional tor router in the TG role. Per the network routing policy, this new ToR router will advertise its own owned prefix. Because the new topology matches the abstraction, the compiled templates will remain the same. However, in the spine router configurations, the match on the global prefix template variable \$GP will be expanded to include the new prefix owned by the ToR. In other words, the concrete configurations obtained after substitution will include an additional match on the new prefix. Unfortunately, this means a small change to the topology can result in many configurations far from the change needing to change too.

The key observation is that the template variables tell us exactly where change can happen. For example, the only way in which the spine routers depend on anything nonlocal is in the prefix template variables. Instead, we replace each match on a template variable (\EG, matching \$GP) with a test on a new community tag that we associate with each template variable. So long as we ensure that routers always add the appropriate tags to the prefixes they originate, then the policies will be equivalent.

Specifically, this ensures that each router has a template that has no dependency on any other non-adjacent router. If we make a change to the concrete network that matches the abstraction, then the templates do not change, and thus only configurations adjacent to the changes must also change.
